Pillar 1 - Student Topic Profile

### 2019-05-15 Pillar 1 - Topic Profile.Rmd
use selected topic model

* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.
* give more weight to 3000-level courses

@@

```{r load, cache.lazy = TRUE}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")

@@

# Course topic profile
```{r gamma_spread}
gamma        <- topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)

beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
```

# Student topic profile
```{r student_TP}
student_TP <- d_transcript_augmented %>%

@@

# Student GPA

@@

```{r}
student_profile_nest <- student_profile %>%

  mutate(profile = profile %>% map(as.matrix))
```

# Regressing grade on TP and GPA

@@

## Lasso
```{r my_cv.glmnet}
my_cv.glmnet <- function(df, alpha = 1, predictors){

@@

  nfold <- min(10, floor(nrow(df) / 3))

@@

```{r fit_lasso, cache = TRUE}
fit_lasso <- tibble(target = course_target) %>%

@@

```{r fit_lasso extract}
fit_lasso <- fit_lasso %>%

@@

Topic chosen by model are related to the course.
```{r}
beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)

i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
beta %>% filter(topic == "Topic 18")
beta %>% filter(topic == "Topic 8" )

i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Business Administration: topic ~ business
beta %>% filter(topic == "Topic 19")

i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
beta %>% filter(topic == "Topic 21") 
beta %>% filter(topic == "Topic 23")

i <- 9; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
beta %>% filter(topic == "Topic 7") 
```

@@

student_profile_nest_app <- student_profile_nest %>%

>>>>

* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.

* give more weight to 3000-level courses

@@

```{r load, cache.lazy = TRUE} 
load("Output/app_model.RDATA")
load("Output/data_student.RDATA")
load("Output/course_current.RDATA")

@@

# Topic Model
```{r gamma_spread}
gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)
beta  <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
remove(app_model)
```

# Students' Topic Expertise
```{r student_TP} 
student_TP <- d_transcript_augmented %>%

@@

# Students' Academic Performance

@@

Remove course enrolments from 2007 from the model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.
```{r}
student_profile <- student_profile %>% filter(Year_numerical != 2007)
```

## Save
```{r save student_TP} 
save(student_profile, file = "Output/student_profile.RDATA")
```
# Regressing grade on TP and GPA

@@

```{r my_cv.glmnet} 
my_cv.glmnet <- function(df, alpha = 1, predictors){

@@

  nfold <- min(10, floor(nrow(df) / 3)) # try nfold = 10

@@

## Model fit
```{r fit_lasso, cache = TRUE} 
fit_lasso <- tibble(target = course_target) %>%

@@

## Extract results
```{r fit_lasso extract} 
fit_lasso <- fit_lasso %>%

@@

Topic chosen by model are related to the course.
```{r}
i <- 1; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
beta %>% filter(topic == "Topic 27")
beta %>% filter(topic == "Topic 62")

i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
beta %>% filter(topic == "Topic 29") 
beta %>% filter(topic == "Topic 64")

i <- 5; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
beta %>% filter(topic == "Topic 16")
beta %>% filter(topic == "Topic 4")
```

@@

student_profile_nest_app <- student_profile %>%

  mutate(profile = profile %>% map(as.matrix)) %>%
